Non-word repetition in Yélî Dnye

### 2021-01-21 manuscript.Rmd
minor

1. add SDs to https://docs.google.com/spreadsheets/d/1f4X7SmP4flhPlCEtvyqp_ERgMp5SC8qHCaMHj93C_FU/edit#gid=44537533
1. add a table with sample studies & languages & their characteristiscs
1. be accurate on what hasn't been done x-ling speaking
1. try to find data on length distribution across languages to see if this fits length differences
1. to the above, add sylable characteristics, inventory size, inventory compactness
1. revise intro
1. revise discussion

@@

pl_stacked=cbind(pl[,1:4],stack(pl[5:8]),stack(pl[9:12]))
colnames(pl_stacked)[5:8]<-c("Median","Length","SD","sdtype")
pl_stacked$Length=gsub("X","",pl_stacked$Length)

@@

mycols = c( 
             "Arabic" = "orange",
             "Italian"   ="black",
             "Tsimane'" = "darkgreen",
             "Yélî Dnye" = "purple")

mywd = c( 
             "Arabic" = 1,
             "Italian"   =1,
             "Tsimane'" = 2,
             "Yélî Dnye" = 4)

>>>>

1. add language chars to https://docs.google.com/spreadsheets/d/1f4X7SmP4flhPlCEtvyqp_ERgMp5SC8qHCaMHj93C_FU/edit#gid=44537533
1. add a table with sample studies & languages & their characteristiscs
1. be accurate on what hasn't been done x-ling speaking
1. try to find data on length distribution across languages to see if this fits length differences
1. to the above, add sylable characteristics, inventory size, inventory compactness
1. revise intro
1. revise discussion
1. improve figure 1?

@@

pl_stacked=cbind(pl[,c("Study","Language","n","Age")],stack(pl[c("X1","X2","X3","X4")]),stack(pl[c("sd1","sd2","sd3","sd4")]))
colnames(pl_stacked)[5:8]<-c("Median","Length","SD","sdtype")
pl_stacked$Length=gsub("X","",pl_stacked$Length)

@@

mycols = c( 
             "Arabic" = "orange",
             "Italian"   ="black",
             "Cantonese"   ="blue",
             "English"   ="green",
            "Tsimane'" = "darkgreen",
             "Yélî Dnye" = "purple")

mywd = c( 
             "Arabic" = 1,
             "Italian"   =1,
             "Cantonese"   =1,
             "English"   =1,
             "Tsimane'" = 2,
             "Yélî Dnye" = 4)
